### 2013-06-29 inst/doc/reml.Rmd
documentation

>>>>

## Why EML?

Archival, open data is great ... blah blah.  Good reuse is all about good Metadata blah blah...

But specifying metadata is typically onerous, time-consuming and error prone.  Your metadata doesn't define your date format/missing value character/etc etc?  What, that's metadata too?  Wouldn't it be nice if someone thought of all the things we should record and just made a template we could use?

Oh, wait, they did.  It's called EML, and it's been around a long time.  Like carved in petroglyphs long time, in the days before a public internet existed.

Oh, you haven't heard of it?  That's probably because what should be a time-saving template appears more like a huge technological barrier best left to tech geeks.   But it isn't.

> Terence Parr once said "being an expert in XML is like being an expert in CSV".

Or at least, it doesn't have to be that way.  We just need better tools.

## Why REML?
